---
title: "Who Gets You to the Gym?"
subtitle: "Personal Social Networks and Gym Attendance among Graduate Students"
date: today
format:
  html:
    toc: true
    toc-depth: 2
    number-sections: true
    code-fold: true
    code-summary: "Show code"
    theme: cosmo
    embed-resources: true
execute:
  echo: true
  warning: false
  message: false
---

```{r setup}
#| include: false
pkgs <- c("tidyverse", "lme4", "lmerTest",
          "car", "ggeffects", "janitor", "modelsummary",
          "ergm")

for (p in pkgs) {
  if (!requireNamespace(p, quietly = TRUE))
    install.packages(p, repos = "https://cloud.r-project.org", quiet = TRUE)
  suppressPackageStartupMessages(library(p, character.only = TRUE))
}

data_dir <- "."

rel_labels <- c("Close friend", "Casual friend", "Family member",
                "Romantic partner", "Coworker/Classmate",
                "Online-only friend", "Other")
```

# Background & Hypotheses

Do the people around you shape how often you go to the gym? This study explores whether graduate students' gym attendance is influenced by **who they know** — the structure and composition of their personal networks — or whether individual motivation is all that matters.

We draw on social support and social influence theories and test two competing explanations:

> **H0 (Null):** Gym attendance is independent of who you know. Individual factors explain everything.
>
> **H1 (Alternative):** People with more exercise-active and supportive contacts go to the gym more often.

------------------------------------------------------------------------

# Data & Sample

Data were collected using **Network Canvas** (v3.1.2), a tool designed for personal network interviews. Each participant:

1.  Answered questions about their own gym habits and motivations
2.  Named up to 15 people who influence their exercise life (across three prompts: gym partners, encouragers, and social media fitness contacts)
3.  Rated each named person on several attributes
4.  Indicated which of those people know each other

This design — called an **egocentric network study** — lets us measure both the individual and their social environment simultaneously.

```{r load-data}
dataDirectoryPath <- data_dir

alterData <- dataDirectoryPath |>
  list.files(full.names = TRUE, pattern = "attributeList_Person.csv") |>
  lapply(\(f) read.csv(f, colClasses = "character")) |>
  bind_rows()

edgelistData <- dataDirectoryPath |>
  list.files(full.names = TRUE, pattern = "edgeList.*\\.csv") |>
  lapply(\(f) read.csv(f, colClasses = "character")) |>
  bind_rows() |>
  filter(!is.na(networkCanvasSourceUUID), !is.na(networkCanvasTargetUUID))

egoData <- dataDirectoryPath |>
  list.files(full.names = TRUE, pattern = "ego.csv") |>
  lapply(\(f) read_csv(f,
                       col_types = cols(networkCanvasCaseID = col_character()),
                       show_col_types = FALSE)) |>
  bind_rows() |>
  arrange(sessionStart) |>
  mutate(
    pid  = sprintf("P%02d", row_number()),
    gender = factor(gender, 1:3, c("Male", "Female", "Other")),
    gym_days          = as.numeric(ego_day_to_gym),
    appearance_motiv  = as.numeric(ego_physical_app),
    achievement_motiv = as.numeric(personal_archieve),
    social_media_freq = as.numeric(ego_motivation_influence)
  ) |>
  select(networkCanvasEgoUUID, pid, gender,
         gym_days, appearance_motiv, achievement_motiv, social_media_freq)

alterData <- alterData |>
  mutate(
    across(c(ni_other_phy, ni_motivate, ni_interaction), as.numeric),
    across(c(ni_relationship_1, ni_relationship_2, ni_relationship_3,
             ni_relationship_4, ni_relationship_5, ni_relationship_6,
             ni_relationship_7), as.logical),
    rel_type = case_when(
      ni_relationship_1 == TRUE ~ "Close friend",
      ni_relationship_2 == TRUE ~ "Casual friend",
      ni_relationship_3 == TRUE ~ "Family member",
      ni_relationship_4 == TRUE ~ "Romantic partner",
      ni_relationship_5 == TRUE ~ "Coworker/Classmate",
      ni_relationship_6 == TRUE ~ "Online-only friend",
      ni_relationship_7 == TRUE ~ "Other",
      TRUE                      ~ "Unknown"
    ),
    rel_type      = factor(rel_type, c(rel_labels, "Unknown")),
    alter_activity = ni_other_phy,
    is_active      = as.integer(ni_other_phy >= 4),
    motivate_score = ni_motivate,
    interact_freq  = ni_interaction
  ) |>
  select(networkCanvasEgoUUID, networkCanvasUUID,
         rel_type, alter_activity, is_active,
         motivate_score, interact_freq)
```

------------------------------------------------------------------------

# Statistical Models

> **N = `r nrow(egoData)` participants, `r nrow(alterData)` named contacts.** All models are exploratory — interpret estimates descriptively, not causally.

------------------------------------------------------------------------

## Part A: What Predicts How Often Someone Goes to the Gym?

We use **OLS regression** at the participant level with three nested models, adding network variables at each step to test whether social network characteristics predict gym attendance beyond individual factors.

```{r ego-model-data}
net_size_df <- alterData |>
  group_by(networkCanvasEgoUUID) |>
  summarise(net_size = n(), .groups = "drop")

density_df <- edgelistData |>
  count(networkCanvasEgoUUID, name = "actual_ties") |>
  right_join(net_size_df, by = "networkCanvasEgoUUID") |>
  mutate(
    actual_ties   = replace_na(actual_ties, 0L),
    possible_ties = net_size * (net_size - 1L) / 2,
    density       = if_else(possible_ties > 0, actual_ties / possible_ties, NA_real_)
  ) |>
  select(networkCanvasEgoUUID, density)

prop_active_df <- alterData |>
  group_by(networkCanvasEgoUUID) |>
  summarise(prop_active = mean(is_active, na.rm = TRUE), .groups = "drop")

entropy_df <- alterData |>
  filter(!is.na(rel_type), rel_type != "Unknown") |>
  count(networkCanvasEgoUUID, rel_type) |>
  group_by(networkCanvasEgoUUID) |>
  mutate(p = n / sum(n)) |>
  summarise(entropy = -sum(p * log(p)), .groups = "drop")

ego_model_data <- egoData |>
  left_join(net_size_df,    by = "networkCanvasEgoUUID") |>
  left_join(density_df,     by = "networkCanvasEgoUUID") |>
  left_join(prop_active_df, by = "networkCanvasEgoUUID") |>
  left_join(entropy_df,     by = "networkCanvasEgoUUID") |>
  mutate(prop_active = replace_na(prop_active, 0)) |>
  filter(!is.na(gym_days))
```

### Model 1 — Individual Factors Only

```{r m1}
m1 <- lm(gym_days ~ gender + appearance_motiv + achievement_motiv,
         data = ego_model_data)
summary(m1)
```

M1 includes only individual-level variables. The overall model is marginally significant (F(3, 34) = 3.80, *p* = .019, R² = 0.25), but no individual predictor reaches conventional significance. Achievement motivation shows the largest effect (β = 0.62), suggesting that exercising for personal goals is associated with more gym days, though the effect is imprecisely estimated at this sample size.

### Model 2 — Adding Network Structure

```{r m2}
m2 <- lm(gym_days ~ gender + appearance_motiv + achievement_motiv
         + density + net_size,
         data = ego_model_data)
summary(m2)
```

Adding network density and size drops the sample to N = 28 (participants needing at least two alters for density to be defined) and the adjusted R² collapses to 0.04. Neither density (β = −0.59) nor network size (β = 0.08) is significant. Network structure adds no explanatory power over individual factors.

### Model 3 — Adding Network Composition

```{r m3}
m3 <- lm(gym_days ~ gender + appearance_motiv + achievement_motiv
         + density + net_size + prop_active + entropy,
         data = ego_model_data)
summary(m3)
```

Network composition variables also fail to reach significance. Notably, the proportion of active contacts carries a *negative* coefficient (β = −1.69), the opposite of H1, though far from significant. Adjusted R² remains at 0.05. Together, Parts A1–A3 provide no support for H1 at the ego level.

### OLS Summary Table

```{r ols-table}
modelsummary(
  list("M1: Individual" = m1, "M2: + Structure" = m2, "M3: + Composition" = m3),
  stars   = c("*" = .1, "**" = .05, "***" = .01),
  gof_map = c("nobs", "r.squared", "adj.r.squared"),
  title   = "OLS Regression — Outcome: Gym days per week",
  notes   = "Reference category: Female. Network variables in M2–M3 test H1."
)
```

Across all three models, no predictor reaches conventional significance and model fit worsens as network variables are added. The evidence is consistent with **H0**: individual factors, not network characteristics in aggregate, drive gym attendance.

------------------------------------------------------------------------

## Part B: What Makes a Contact a Good Motivator?

Rather than asking who goes to the gym more, we now ask which contacts provide the most motivation to exercise. The outcome is `motivate_score` (1–5). Because contacts are nested within participants, we use **random-intercept multilevel models**.

```{r merged-data}
merged_data <- egoData |>
  inner_join(alterData, by = "networkCanvasEgoUUID") |>
  mutate(motivate_score = na_if(motivate_score, -1))
```

### Model 1 (Null) — Partitioning Variance

```{r mlm-null}
model1 <- lmer(motivate_score ~ (1 | networkCanvasEgoUUID),
               data = merged_data)
summary(model1)
```

```{r icc-text}
#| include: false
vc  <- as.data.frame(VarCorr(model1))
icc <- round(vc$vcov[1] / sum(vc$vcov), 3)
```

ICC = **`r icc`** (`r scales::percent(icc)`). About 29% of the variance in motivation scores is attributable to which participant was interviewed; the remaining 71% reflects differences *between contacts within the same person*. This within-person variance is large enough to justify modeling contact-level predictors.

------------------------------------------------------------------------

### Model 2 — Contact-Level Predictors

```{r mlm-alter}
model2 <- lmer(motivate_score ~ is_active + interact_freq
               + (1 | networkCanvasEgoUUID),
               data = merged_data)
summary(model2)
```

Both contact-level predictors are highly significant. Being rated as exercise-active (score ≥ 4) is associated with a **0.76-point higher motivation score** (β = 0.76, *p* \< .001) — a meaningful shift on a 1–5 scale. More frequent interaction also predicts higher motivation (β = 0.18, *p* = .002). Adding these two predictors reduces the between-person variance by more than half (from 0.336 to 0.159), suggesting that who participants name largely drives the between-person variation seen in the null model.

### Model 3 — Adding Participant-Level Controls

```{r mlm-full}
model3 <- lmer(motivate_score ~ is_active + interact_freq
               + gym_days + gender
               + (1 | networkCanvasEgoUUID),
               data = merged_data)
summary(model3)
```

After controlling for the participant's own gym frequency and gender, the `is_active` effect **grows to β = 0.84** (*p* \< .001) and `interact_freq` remains significant (β = 0.14, *p* = .017). Neither `gym_days` nor `gender` reaches significance, ruling out the simplest selection story — the contact's own activity level, not the participant's habits or demographics, is what drives motivational value.

### Predicted Motivation by Contact Activity Level

```{r ggpredict-active}
#| fig-height: 4
ggpredict(model3, "is_active") |>
  plot() +
  labs(title = "Predicted motivation score: active vs. less active contacts",
       subtitle = "Based on Model 3; shaded area = 95% confidence interval",
       x = "Contact is exercise-active (0 = No, 1 = Yes)",
       y = "Predicted motivation score (1–5)") +
  theme_classic()
```

The predicted motivation score is approximately **0.84 points higher** for exercise-active contacts, holding interaction frequency, participant gym frequency, and gender constant. The confidence intervals for the two groups do not overlap, indicating a robust and practically meaningful difference.

------------------------------------------------------------------------

# ERGM — Do Active Alters Cluster Together?

The multilevel models treat each alter independently. An ERGM asks a structurally different question: **does the pattern of ties *among* alters itself carry signal** — specifically, do exercise-active contacts tend to know each other, or do similarly active people cluster together?

We pool all alter-alter edges across ego networks into a single undirected network and fit ERGMs with each alter's physical activity rating (1–5) as a vertex attribute.

```{r ergm-build}
alters_ergm <- alterData |> filter(!is.na(alter_activity))

valid_uuids <- alters_ergm$networkCanvasUUID
edges_ergm  <- edgelistData |>
  filter(networkCanvasSourceUUID %in% valid_uuids,
         networkCanvasTargetUUID  %in% valid_uuids)

v_idx    <- setNames(seq_len(nrow(alters_ergm)), alters_ergm$networkCanvasUUID)
edge_src <- v_idx[edges_ergm$networkCanvasSourceUUID]
edge_tgt <- v_idx[edges_ergm$networkCanvasTargetUUID]
ok       <- !is.na(edge_src) & !is.na(edge_tgt)

net_pool <- network.initialize(nrow(alters_ergm), directed = FALSE)
network::add.edges(net_pool, edge_src[ok], edge_tgt[ok])
network::set.vertex.attribute(net_pool, "alter_activity", alters_ergm$alter_activity)
```

### Model 1 — Baseline Density

```{r ergm1}
ergm1 <- ergm(net_pool ~ edges)
summary(ergm1)
```

The baseline log-odds of a tie is −3.44, implying a network density of roughly 3%. This is expected: most pairs of contacts across different ego networks share no direct connection.

### Model 2 — Activity as a Node Covariate

```{r ergm2}
ergm2 <- ergm(net_pool ~ edges + nodecov("alter_activity"))
summary(ergm2)
```

`nodecov` captures the total activity level of a dyad. Its negative coefficient (β = −0.24, *p* \< .001) indicates that, unconditionally, pairs where both alters are highly active are *less* likely to be tied than chance would suggest. AIC drops from 1854 to 1822, confirming improved fit, but the direction hints that high activity alone does not predict connection — something about similarity may matter more.

### Model 3 — Activity Homophily

```{r ergm3}
ergm3 <- ergm(net_pool ~ edges + nodecov("alter_activity") + absdiff("alter_activity"))
summary(ergm3)
```

Adding `absdiff` — the absolute difference in activity levels between a pair — substantially improves fit (AIC: 1763). Its negative coefficient (β = −0.58, *p* \< .001) confirms **activity homophily**: alters with *similar* activity levels are significantly more likely to know each other. The `nodecov` term remains negative, suggesting that once homophily is accounted for, raw activity level *per se* does not increase connectivity. Together, Model 3 shows that exercise-active contacts tend to cluster with other similarly active people — a structural pattern that may reinforce the motivational effects observed in Part B.

------------------------------------------------------------------------

# Discussion

This study examined whether personal social networks shape gym attendance among graduate students, using ego-centric network data collected via Network Canvas.

At the **participant level** (Part A), no network variable — density, size, proportion of active contacts, or relationship diversity — significantly predicted weekly gym frequency. Individual achievement motivation was the strongest predictor (β = 0.62), though it did not reach significance in this small sample. The evidence across all three OLS models is consistent with **H0**: who you know in the aggregate does not determine how often you work out.

At the **contact level** (Part B), a consistent and robust pattern emerged. Contacts rated as highly physically active provided significantly stronger motivation to exercise (β = 0.84, *p* \< .001, Model 3), and this effect *strengthened* after accounting for participant characteristics — ruling out a straightforward selection explanation. Interaction frequency also contributed (β = 0.14, *p* = .017), though its effect was smaller. Exercise support appears to be a **dyadic phenomenon**: it depends on the specific relationship rather than the overall composition of one's network.

The **ERGM results** (Part C) add a structural layer: exercise-active alters tend to cluster with similarly active contacts (absdiff β = −0.58, *p* \< .001), forming homophilic micro-clusters within ego networks. This structural tendency may amplify the contact-level motivational effects — being embedded among similarly active people could reinforce exercise norms through repeated, mutual exposure.

**Limitations:** Small sample (N = `r nrow(egoData)`), cross-sectional design, and the constraints of egocentric data — which cannot distinguish social influence from selection, nor fully capture the ego's broader network context.
